A Pilot Multicenter Cluster Randomized Trial to Compare The Effect of Trauma Life Support Training Programs on Patient and Provider Outcomes

### 2024-01-05 pilot-publication/lab-book.Rmd
Work on extracting data from gt tables

```{r}
## Load outcome results
outcome.results <- readRDS("outcome-results.rds")

@@

>>>>

```{r}
## Load outcome results
outcome.results <- readRDS("outcome-results.Rds")

@@

## Access data from gt table object

```{r}
gt.table <- tables[[1]][[1]]
str(gt.table$`_data`, max.level = 1)
gt.table$`_data`
gt.table$`_styles`
```

### 2024-01-05 pilot-publication/manuscript.Rmd
Work on extracting data from gt tables

```{r, echo = FALSE}
post.training.outcomes.table <- outcome.results.tables$ci.level.0.95[["Outcomes in all patients after training, by treatment arm"]]
m30d.atls <- inline_text(post.training.characteristics.table,
  variable = outcomes__alive_after_30_days,
  level = "Yes",
  column = "ATLS"
)
```

>>>>

```{r, echo = FALSE}
post.training.outcomes.table <- outcome.results.tables$ci.level.0.95[["Outcomes in all patients after training, by treatment arm"]]
m30d.atls <- inline_text(post.training.characteristics.table,
  variable = outcomes__alive_after_30_days,
  level = "Yes",
  column = "ATLS"
)
m30d.ptc <- inline_text(post.training.characteristics.table,
  variable = outcomes__alive_after_30_days,
  level = "Yes",
  column = "PTC"
)
```
